---
title: "README"
output: github_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = here::here())
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

pacman::p_load(tidyverse,
               runjags)
```

# Article information

Title: Seasonal timing of ecosystem linkage mediates life-history variation in a salmonid fish population

Author: Ueda R, Kanaiwa M, Terui A, Takimoto G, Sato T

Journal: Ecology

# Analytical flow

This repository covers statistical procedures for the spatial CJS model.
Run `code/run_model_scjs.R` to reproduce the reported results.
Output data are visualized in scripts with `figure_` prefix.

# File description

```{r}

setwd(str_remove(normalizePath("."), "\\\\rmd"))
source(here::here("rmd/table_rmd.R"))
knitr::kable(df_fnm)

```

# Session information

```{r}
sessionInfo()
```

